Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-12 Manuscript/manuscript.tex
New abstract and small changes in the text
Small update to the stochiometry section: added a few data (matti's C36 sim and mine sim with NaCl)

The residence time of \ce{Ca^{2+}} bound to a POPC membrane 
is experimentally estimated to be lower than $10\,\mu\mathrm{s}$~\cite{altenbach84}. 
From a recent theoretical work with long simulations 
(Fig. S17 in \citenum{javanainen17} -- C36 with MK Ca2+, any other model, either different cation or Slipids/C36, just such calcium)
this time can be roughly estimated -- get the simulation from \url{https://doi.org/10.5281/zenodo.259376} and analyze it -- 
in the order of $1$--$10\,\mu\mathrm{s}$~\cite{javanainen17}. 
This is in contrast to our model, ECC-lipids, 
which estimates the residence time of calcium bound to a POPC membrane to be 
smaller than $53\,\mathrm{ns}$ for 90\% of the time a cation is in a membrane-bound state. 
i.e. at least two orders of magnitude lower than previous estimates.
In addition, the longest observed residence time in our simulation is $120\,\mathrm{ns}$, 
which is well below the length of our simulations.
This is unfortunately not the case of many theoretical works,
where the residence time cannot be estimated,
or the simulation has not even decorrelated from it's 
initial condition with a population of bound/unbound cations \cite{catte16}, 
because it is limited by the simulation length, 
even though it can be very long (order of $\mu\mathrm{s}$) in some works, e.g. reference~\citenum{javanainen17}. 
Increasing time scales to the order of $\mu\mathrm{s}$ 
doesn't help to alleviate such a problem in current lipid models \cite{javanainen17}. %and also \cite{catte16}, but same simulation was used. 
Such a finding changes the point of view of calcium binding from
very tight long-term stable binding with rare exchanges to 
a relatively frequent exchange of cations 
in equilibrium between membrane and solvent. 
A histogram of residence times from our simulations is in Fig.~S\ref{fig:hist_residence_times} in SI. 
\todo{JOE: Plot a histogram of residence times based on our simulations and simulation from \citenum{javanainen17} and put it into SI.
Add data for Na+. }

>>>>

The residence time of \ce{Ca^{2+}} bound to a POPC membrane 
is experimentally estimated to be lower than $10\,\mu\mathrm{s}$~\cite{altenbach84}. 
From a recent theoretical work with long simulations 
(Fig. S17 in \citenum{javanainen17} -- C36 with MK Ca2+, any other model, either different cation or Slipids/C36, just such calcium)
this time can be roughly estimated -- get the simulation from \url{https://doi.org/10.5281/zenodo.259376} and analyze it -- 
in the order of $1$--$10\,\mu\mathrm{s}$~\cite{javanainen17}.

Quick result (Matti C36 with CaClMK, 800ns total):
90\% of bound residence time is smaller than 787 ns, 
The longest is 800 ns

This is in contrast to our model, ECC-lipids, 
which estimates the residence time of calcium bound to a POPC membrane to be 
smaller than $53\,\mathrm{ns}$ for 90\% of the time a cation is in a membrane-bound state. 
i.e. at least two orders of magnitude lower than previous estimates.
In addition, the longest observed residence time in our simulation is $120\,\mathrm{ns}$, 
which is well below the length of our simulations.
This is unfortunately not the case of many theoretical works,
where the residence time cannot be estimated,
or the simulation has not even decorrelated from it's 
initial condition with a population of bound/unbound cations \cite{catte16}, 
because it is limited by the simulation length, 
even though it can be very long (order of $\mu\mathrm{s}$) in some works, e.g. reference~\citenum{javanainen17}. 
Increasing time scales to the order of $\mu\mathrm{s}$ 
doesn't help to alleviate such a problem in current lipid models \cite{javanainen17}. %and also \cite{catte16}, but same simulation was used. 
Such a finding changes the point of view of calcium binding from
very tight long-term stable binding with rare exchanges to 
a relatively frequent exchange of cations 
in equilibrium between membrane and solvent.

Interestingly, \ce{Na+} cations exhibit much more rapid exchange between membrane and solvent.
The residence time of sodium bound to a POPC membrane is
smaller than $2\,\mathrm{ns}$ for 90\% of the time it is bound to the membrane 
with the longest measured bound time being $13\,\mathrm{ns}$.

A histogram of residence times from our simulations is in Fig.~S\ref{fig:hist_residence_times} in SI. 
\todo{JOE: Plot a histogram of residence times based on our simulations and simulation from \citenum{javanainen17} and put it into SI.
Add data for Na+. }
